%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Shashank}{Singh}{
\href{mailto:ssingh512@bloomberg.net}{ssingh512@bloomberg.net} | 480.465.2265 | \href{mailto:shashanksingh28@gmail.com}{shashanksingh28@gmail.com}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 
\hspace{+0.5mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Arizona State University}
\descript{M.S in Computer Science}
\location{Aug 2017 | Tempe, AZ}
\location{ GPA: 4.0 / 4.0 }
\sectionsep

\subsection{Mumbai University}
\descript{B.E in Information Technology}
\location{May 2012 | Mumbai, India}
Sardar Patel Institute of Technology
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hspace{+0.5mm}
\section{Links} 
Github:// \href{https://github.com/shashanksingh28}{\bf shashanksingh28} \\
LinkedIn://  \href{https://www.linkedin.com/in/shashankhsingh}{\bf shashankhsingh}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hspace{+0.5mm}
\section{Skills}
\subsection{Programming}

\location{Proficient:}
\textbullet{} Python \\
\textbullet{} Javascript \\
\textbullet{} C++ \\
\textbullet{} SQL \\

\location{Familiar:}
\textbullet{} C\# \\
\textbullet{} Machine Learning \& Statistics \\
\textbullet{} Bash Scripts \\
\textbullet{} Java \& Hadoop \\
\sectionsep

\subsection{Frameworks \& Tools}
\textbullet{} Numpy, Pandas, Scikit-Learn\\
\textbullet{} NodeJS \& VueJS \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hspace{+0.25mm}
\section{Coursework}
\location{Graduate:}
Fundamentals of Statistical Learning\\
Game Theory and Applications\\
Statistical Machine Learning\\
Adaptive Web\\
Software Security\\
Artificial Intelligence \\
Natural Language Processing\\
Masters Thesis
\sectionsep

\section{Activities}
HackArizona 2017,Best use of Watson platform (Sentiment Analysis)\\
Chess tournament organizer (Barclays)\\
Lead : Plan-India Micro-finance App\\
Tech Lead : Undergrad Cultural Fest\\
% Admin Head : Undergrad Student body\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 
\hspace{+0.5mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Bloomberg}
\descript{| Software Engineer - Data Technologies}
\location{June 2017 – Current | Princeton, NJ}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Trained in C++, Javascript and Bloomberg Tech Stack.
\item Created an AVRO schema driven web form generator (with some extended DSL) so that analysts don't need engineers to create data entry forms.
\item Continously enhancing Business Rule Engine (BRE), enabling anaysts to write their data quality checks on a Python based micro-service framework. Also working on making BRE scalable to batch loads with worklfow specific configurations.
\end{tightemize}
\sectionsep

\runsubsection{Advantage xPO (Client: AMEX)}
\descript{| RA - Digital Acquisitions}
\location{May 2016 – Aug 2016 | Phoenix, AZ}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Improved site visit model evaluation by incorporating log data and reducing lag by 3 days with end to end automation.
\item Removed manual dependencies in dashboard monitoring by creating a config driven, subscription based email alert system for detecting anomalies.
\item Led the development of modeling pipeline for US site personalization and integrated modules from data scientists. Developed dashboard for continuous quality checks in the pipeline.
\item Analyzed Zip data and checked feasibility of mapping Zip5 from IP addresses.
\end{tightemize}
\sectionsep

\runsubsection{Arizona State University}
\descript{| Developer \& Teaching Assistant}
\location{Oct 2015 – May 2017 | Tempe, AZ}
\begin{tightemize}
\item Improved ASU mobile app with 3 bug fixes and contributed to game-day experience module based on geo-fencing.
\item Analyzed potential areas of leverage between Salesforce and Mobile teams.
\item Teaching Assistant for Into. to Soft. Eng. class responsible for conducting recitation sessions to help students understand concepts with examples.
\end{tightemize}
\sectionsep

\runsubsection{Barclays}
\descript{| Technology Analyst}
\location{July 2012 – June 2015 | Pune, India}
\begin{tightemize}
\item Developed a C\# based in-house, configurable ETL solution for .NET projects in Global Tax Team.
\item Evaluated performance of Bulk File Payment Processing system and identified problem areas.
\item Migrated 3 tax applications in a challenging 2 month time-line.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects \& Research}
\begin{itemize}
\item CodeReco: An intelligent code recommender system (Masters thesis) that recommended Java method snippets based on both syntactic and semantic features from mined samples.
\item Improved accuracy of the \href{http://www.isi.edu/publications/licensed-sw/fanseparser/}{fanparser solution} for \href{http://www.clres.com/PrepSemeval2007.html}{Preposition Sense Disambiguation} task by incorporating word embeddings (Word2Vec) and numerical features. Accuracy increased from 88.5\% to 89\%.
\item AutoEncoder: Developed an auto-encoder neural net from scratch which can be configured in number of nodes and hidden layers. Used to learn a lossy compression of 32x32 facial images in a 216 hidden layer activations.
\end{itemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\section{Publications} 
%\renewcommand\refname{\vskip -1.5cm} % Couldn't get this working from the .cls file
%\bibliographystyle{abbrv}
%\bibliography{publications}
%\nocite{*}

\end{minipage} 
\end{document}  \documentclass[]{article}
